Joint photometric modeling for improved measurements in imaging surveys.

### 2014-11-18 documents/paper/ms_v0.0.tex
more text

>>>>

We emphasize that the method we present here is just a toy example of how one 
might improve photometric measurements in astronomical surveys.  By no means do
we believe that this is the best or only way to build a hierarchical model for 
the photometry, however, it does have the property of being simple,
interpretable, and yet quite flexible.  For a ``production'' level set of
posteriors there would still be much to sort out, including ---

\begin{itemize}
\item What data should be used for training the XD model?
\item What are the optimal number of XD components?
\item Which mean values of the mixture should be fixed
\item Which covariances should be diagonal?
\item What are the best features to include model?
\item What, if any, features should be included that are outside the survey
data?
\end{itemize}

All such questions would be straightforward to answer using cross validation,
either on left out ``test'' data or higher signal-to-noise data.  One of the
main reasons that we have not done so here is that the correct metric for any
cross validation approach depends on the scientific goals of the experiment.  
Large surveys can likely define a set of such metrics that meet much of their 
users goals, but there may still be cases where individuals may want to define
their own models.  Finally, we do not argue that posterior values should 
replace photometric measurements in all cases.  Indeed, in the case transient
or varying objects this would likely be a bad idea.  Additionally, it may
hinder the discovery of rare types of objects since the prior would drive the
measurments to values like more common sources.
